Assessing Replenishing Population

### 2023-03-01 minos/validation/replenishing.Rmd
Added to validation Makefile and made some paths relative instead of absolute

```{r}
# Replenishing data
repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')

# scotland replenishing
#scot.repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
```

>>>>

```{r}
# Replenishing data
repl <- read.csv('Minos/data/replenishing/replenishing_pop_2019-2070.csv')

# scotland replenishing
#scot.repl <- read.csv('Minos/data/replenishing/scotland/replenishing_pop_2019-2070.csv')
```
